Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-28 doc/main_jfm.tex
working on shear

\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{N58_0.pdf}
\includegraphics[width=0.3\textwidth]{N58_vel_0.pdf}\\
\includegraphics[width=0.3\textwidth]{N58_20000.pdf}
\includegraphics[width=0.3\textwidth]{N58_vel_20000.pdf}
  \caption{\label{figure3} A Janus-vesicle suspended in a shear flow
  with shear rate $\chi=0.0025$: (a) Initial configuration of 58-body
  Janus-vesicle where black arrows are the particle orientations. (b)
  The particle velocities and streamlines of the configuration in (a).
  Streamlines are plotted in the background as solid curves. Red arrows
  represent the particle velocities. (c) Deformed Janus-vesicle at
  $t=4000$. At this configuration the Janus-vesicle is tank-treading.
  (d) The particle velocities and streamlines of the configuration in
  (c). The background colors in panels (a) and (c) represent the
  strength of the hydrophobic attraction potential. The blue region
  shows no action and the red region in the bilayer gives the strongest
  action.}
\end{figure}
%
%
\todo[inline]{Bryan left off here}
In order to extract more physical properties of the proposed model, we
track the total length of the bilayer structure, the reduced area over
the time, and the excess length. Here the enclosed area and the total
length of the structure are calculated from the midplane.  These results
are shown in Figure~\ref{figure4} where we compare results from the use
of a set of shear rates $\chi=\{0.002,0.0025,0.003,0.0035\}$.  The
reduced area is given by $A^* = 4\pi A/L^2$ where $A$ the area, and $L$
the total length of the Janus-vesicle with respect to the midplane.
Furthermore, the excess length is given by
$\Delta=L/\sqrt{A^*/\pi}-2\pi$.  Since the starting configuration is
close to a circular shape, the reduced area decreases from a value very
close to $1$. For the test cases in Figure~\ref{figure4}, the smooth
curves in panel (a) are fitted using an exponential model given by $A^*
= a_0 + b_0 \exp(-kt)$. Panel (b) shows that the decay rate $k$ is
independent of the shear rate when the shear is above a threshold and
the terminal reduced areas for each case of the shear rates are given in
the inset. It is also clear that a slower shear rate generates a higher
terminal reduced area and has a faster convergence then the high shear
rate cases.  With a converging total arc length as shown in panel (c), a
slower shear rate also produces a smaller excess length shown in panel
(d).  In summary, the small oscillations in all results are due to the
granularity of the Janus-vesicle which tend to having slightly
non-smooth curves in simulations. Overall the total lengths of the
bilayer have the same converging value in all test shear rates.
Moreover, based on the numerical experiments, we observe that the reduce
area converges relatively early when the shear rate is lower than
$\chi=0.003$.

\begin{figure}
\begin{center}
\hspace{-0.6cm}
\includegraphics[height=2in]{ReducedArea.pdf}
\hspace{0.6cm}
\includegraphics[height=2in]{DecayRate.eps}\\
\includegraphics[height=2in]{ArcLength.pdf}
\includegraphics[height=2in]{ExcLength.pdf}
\end{center} 
  \caption{(a) Total arc lengths of the midplanes over time in cases of different shear rates; (b) From exponential fits in panel (a), we obtain the decay rate $k$ for a number of different shear rates. The inset plots the terminal reduced areas; (c) Reduced area transitions over time; (d) Excess length of the midplanes.
For all panels, a set of shear rates $\chi=\{0.002,0.0025,0.003,0.0035\}$ is used in simulations. 
The legend in panel (d) applies to both panels (a) and (c). 
  }
    \label{figure4}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{N58_0.pdf}
\includegraphics[width=0.3\textwidth]{N58_vel_0.pdf}\\
\includegraphics[width=0.3\textwidth]{N58_20000.pdf}
\includegraphics[width=0.3\textwidth]{N58_vel_20000.pdf}
  \caption{\label{figure3} A Janus-vesicle suspended in a shear flow
  with shear rate $\chi=0.0025$: (a) Initial configuration of 58-body
  Janus-vesicle where black arrows are the particle orientations. (b)
  The particle velocities and streamlines of the configuration in (a).
  Streamlines are plotted in the background as solid curves. Red arrows
  represent the particle velocities. (c) Deformed Janus-vesicle at
  $t=4000$. At this configuration the Janus-vesicle is tank-treading.
  (d) The particle velocities and streamlines of the configuration in
  (c). The background colors in panels (a) and (c) represent the
  strength of the hydrophobic attraction potential. The blue region
  shows no action and the red region in the bilayer gives the strongest
  action.}
\end{figure}
%
%

To extract additional physical properties of the proposed model, we
compute the total length, reduced area, and excess length of the bilayer
structure. The enclosed area and the total length of the structure are
calculated from the midplane. The reduced area is $A^* = 4\pi A/L^2$
where $A$ the area, and $L$ the total length of the Janus-vesicle, and
the excess length is $\Delta=L/\sqrt{A^*/\pi}-2\pi$.
Figure~\ref{figure4} shows these quantities for a Janus-vesicle
suspended in a shear flow with shear rates
$\chi=\{0.002,0.0025,0.003,0.0035\}$. Since the starting configuration
is nearly circular, the reduced area decreases from an initial value
close to $1$. The smooth curves in panel (a) are best fits of the
exponential model $A^* = a_0 + b_0 \exp(-kt)$. Panel (b) shows that the
decay rate $k$ is independent of the shear rate for sufficiently large
shear rates, and the terminal reduced areas of each case are shown in
the inset. We see that lower shear rates generate a higher final reduced
area. In particular, we observe that the reduce area converges
relatively early when the shear rate is lower than $\chi=0.003$. 
%and has a faster convergence than the high shear rate cases.
Panel (c) shows that the total arc length remains constant for all time
with all four shear rates. Combining the behavior of the reduced area
and the total arc length, the excess length must increase in time and be
larger for higher shear rates as observed in panel (d). In all these
results, there are oscillations that can be explained by the granularity
of the Janus-vesicle which results in a midplane that is non-smooth.
%Overall the total lengths of the bilayer have the same converging value
%in all test shear rates.

\begin{figure}
\begin{center}
\hspace{-0.6cm}
\includegraphics[height=2in]{ReducedArea.pdf}
\hspace{0.6cm}
\includegraphics[height=2in]{DecayRate.eps}\\
\includegraphics[height=2in]{ArcLength.pdf}
\includegraphics[height=2in]{ExcLength.pdf}
\end{center} 
  \caption{\label{figure4} (a) Total arc lengths of the midplanes over
  time for four shear rates. (b) From exponential fits in panel (a), we
  obtain the decay rate $k$ for a number of different shear rates. The
  inset plots the terminal reduced areas. (c) Reduced area transitions
  over time. (d) Excess length of the midplanes. For all panels, a set
  of shear rates $\chi=\{0.002,0.0025,0.003,0.0035\}$ is used in
  simulations. The legend in panel (d) applies to both panels (a) and
  (c).}
\end{figure}
